EoS-insensitive relations after GW170817

### 2019-01-31 paper/bin-love-after-gw170817.tex
addressing comments

{\ny{Just some general comments so that we don't forget:
\begin{itemize}
\item The EoS-insensitive relations are called ``binary Love'', ``I-Love-Q'', ``C-Love'' and ``R-Love.'' There is no need to call them ``binary Love EoS-insensitive relations.'' That's too verbose and not what they are called in the literature. I am ok with describing these relations as EoS-insensitive instead of approximately universal, but let's not change the names. 
\item There is some serious tidying up that needs to be done to all of the text. Specifically, there are missing prepositions, like ``the'', in lots of places that makes the reading a bit choppy and we can improve. Zack, when you have a chance, please do a detail read through and fix the flow as much as you can. 
\item Eventually, we need to discuss the abstract and the intro in more detail. 
\item Let's not forget to check the acknowledgments for funding sources. 
\item Let's do a spell check. 
\item Let's remove all commented out text.  
\end{itemize}
}}
The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Abrahamyan:2012gp,Horowitz:2012tj,Horowitz:2013wha}), making NSs ideal laboratories for constraining ultra dense nuclear matter.

@@

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also present new R-Love relations displaying the relationship between NS radius and tidal deformability, showing maximum EoS variability of $18.88\%$ from the fit discussed in Sec.~\ref{sec:clove}.
Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love relations will become necessary.
Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal waveform, rather than the PhenomD + 6PN tidal correction to demonstrate the effect of waveform mismodeling.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circles) in the extraction of $\lambda_0$ from GW170817 (O2 detector sensitivity) as if it were observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (turquoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in improved binary Love relations (indigo dashed line) for Voyager CE, and ET.
These results are further tabulated in Table~\ref{tab:variances}.
Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the effect of waveform mismodeling uncertainties.
The single-detection uncertainties are shown by unfilled blue circles, while the combined detection uncertainties are outlined by dashed maroon.
}
\label{fig:stackedFisher}
\end{figure}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.eps}
\end{center}
\caption{
Small representative sets of the unconstrained (dotted) and constrained (solid) EoSs used in this analysis. 
The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constraints applied.
The following restrictions were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
}
\label{fig:eos}
\end{figure}

@@

\begin{table*}
\centering
\caption{
I-Love-Q, C-Love, and R-Love relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
}\label{tab:ILQfitNew}
\begin{tabular}{ c  c  | c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313$ & $1.287$ & $0.09888$ & $-2.300$ & $-1.347$ & $0.3857$ & $-0.02870$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.555$ & $-2.122$ & $2.72$ & $-1.491$ & $0.8644$ & $-0.1428$ & $-1.397$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.008921$ & $10.59$ & $-37.46$ & $43.18$ & $-2.361$ & $1.967$ & $-0.5678$\\
 $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & $-383.5$ & $192.5$ & $-811.1$\\
 $R$ & $\Lambda$ & $-1/40$ & $8.575$ & $-10.55$ & $17.32$ & $-29.76$ & $-9.978$ & $21.91$ & $-31.77$\\
\hline
\hline
\end{tabular}
\end{table*}

@@

\begin{table}
\centering
\caption{
Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
 $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
 \hline
 $C-\Lambda$ & $0.065$ & $0.07198$ & $0.02169$\\
 $R-\Lambda$ & -- & $0.4983$ & $0.1792$\\
 \hline
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5724$} & \multirow{2}{*}{$0.2140$}\\
 $(q=0.90)$ & & &\\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447$} & \multirow{2}{*}{$0.08284$}\\
  $(q=0.7)$ & & &\\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.03841$} & \multirow{2}{*}{$0.01823$}\\
  $(q=0.50)$ & & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

\subsection{C-Love Relations}\label{sec:clove}
In this section we consider approximately EoS-insensitive C-Love relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
In addition, we show the R-Love relations, giving the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.

@@

Additionally, Fig.~\ref{fig:rlove} displays the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
Similar to the fits performed for the I-Love-Q and C-Love relations, we fit the R-Love relations to Eq.~\ref{eq:ILQfitNew}.
In this case, we utilize the same Newtonian control factor found in Eq.~\ref{eq:cloveFit} for the C-Love relations, substituting the NS mass with the polytropic form $M\propto R^{(3-n)/(1-n)}$~\cite{Shapiro:MRpolytrope}.
Noting that most physical EoSs obey approximate polytropic indices between $0.50$ and $1.00$, as shown in Ref.~\cite{Yagi:binLove}, we choose a central value of $n=0.75$ for use in this analysis, resulting in $M\propto R^9$.
Absorbing the proportionality constant into $K_{R\Lambda}$ gives the approximate Newtonian relationship as:
\begin{equation}
R^N \approx K_{R\Lambda}\Lambda^{-1/40}.
\end{equation}
The results of this fit are displayed in Tab.~\ref{tab:ILQfitNew}, and the maximal EoS variability is again shown in Tab.~\ref{tab:maxVar}.
Previously, this relation observed large relative uncertainties on the order of $\sim50\%$ on the mapping from tidal deformability to radius, as can be seen by the unconstrained EoSs in Fig.~\ref{fig:rlove}.
However, upon the restriction to soft EoSs conforming to GW170817, we observe a large suppression in EoS variability to the order of $\sim20\%$.
This results in new EoS-insensitive relations, with relative uncertainties on the same scale as found in the binary Love relations discussed below in Sec.~\ref{sec:binary}.
\begin{figure}
\begin{center} 
\includegraphics[width=1\columnwidth]{RL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:clove} but for the R-Love relationship between the NS radius and tidal deformability.
In this figure, we also construct fits to  Eq.~\ref{eq:ILQfitNew}, limiting to the Newtonian case $R \sim M\Lambda^{1/5}$, with $M\sim R^{(3-n)/(1-n)}$ for polytropic index $n$.
Observe how the fractional difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
Also shown in this figure is the hybrid star R-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
}
\label{fig:rlove}
\end{figure}

@@

\subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
In this section, we consider the effect of hybrid star EoSs on the C-Love and R-Love relations.
Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.

Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs under the fitting conditions for each case described above. 
We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
From this, we similarly conclude that hybrid stars do obey the C-Love relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
We observe similar results for the case of R-Love relations, as seen by the dashed green curves in Fig.~\ref{fig:rlove}.
Here, the hybrid stars show a maximal fractional difference of $30.82\%$ from the constrained EoS fits, still much smaller than the unconstrained EoSs variation.

@@

In this section, we investigate the residuals on $\lambda_0(\Lambda_a,\Lambda_s,q)$ in order to marginalize over the intrinsic error in the binary Love relations.
In particular, we restrict our focus to only the constrained set of EoSs.
Residuals on $\lambda_0$ are computed as $\lambda_0^{\text{fit}}-\lambda_0^{\text{true}}$, where $\lambda_0^{\text{true}}=\lambda_0(\Lambda_a,\Lambda_s,q)$ corresponds to the true values predicted by the sample EoSs, and $\lambda_0^{\text{fit}}=\lambda_0(\Lambda_a^{\text{fit}}(\Lambda_s,q),\Lambda_s,q)$ corresponds to the values obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
Following Ref.~\cite{Katerina:residuals}, we assume the residuals on $\lambda_0$ observe a Gaussian distribution with mean and standard deviation given by:
\begin{align}
\mu_{\lambda_0}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
\sigma_{\lambda_0} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
\end{align}
Similar to Ref.~\cite{Katerina:residuals}, we fit the individual components to the following power functions:
\begin{align}
\mu_{\Lambda_s}(x) &= \mu_1 x + \mu_2, \label{eq:margFit1}\\ 
\mu_{q}(x) &= \mu_3 x^2 + \mu_4 x + \mu_5, \label{eq:margFit2}\\ 
\sigma_{\Lambda_s}(x) &= \sigma_1 x^{5/2} + \sigma_2 x^{3/2} +  \sigma_3 x^{1/2} + \sigma_4, \label{eq:margFit3}\\ 
\sigma_{q}(x) &= \sigma_5 x^3 + \sigma_6 x^2 + \sigma_7 x + \sigma_8. \label{eq:margFit4}
\end{align}
The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Tab.~\ref{tab:marginalized}, and Fig.~\ref{fig:qLsResiduals} shows the $\lambda_0$ residuals binned in both q and $\Lambda_s$, highlighting the error weights across the $(q,\Lambda_s)$ parameter space.
Observe how $q\sim0.5$ and $\Lambda_s\sim2000$ obtain the highest errors, while the low and high values of $q$ and $\Lambda_s$ have minimal uncertainties.

\begin{table}
\centering
\caption{
Coefficients to the fits given by Eqs. (\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\lambda_0$ in the improved binary Love relations presented in this paper.
}\label{tab:marginalized}
\addtolength{\tabcolsep}{1pt} 
\begin{tabular}{ c | c || c | c}
\hline 
\noalign{\smallskip}
$\mu_1$ & $-1.016\times10^{-29}$ & $\sigma_1$ & $-1.195\times10^{-33}$\\
$\mu_2$ & $5.376\times10^{-27}$ & $\sigma_2$ & $4.056\times10^{-30}$\\
$\mu_3$ & $-6.850\times10^{-25}$ & $\sigma_3$ & $5.699\times10^{-27}$\\
$\mu_4$ & $1.024\times10^{-24}$ & $\sigma_4$ & $-1.334\times10^{-26}$\\
$\mu_5$ & $-3.680\times10^{-25}$ & $\sigma_5$ & $7.168\times10^{-24}$\\
 &  & $\sigma_6$ & $-1.595\times10^{-23}$\\
 &  & $\sigma_7$ & $1.098\times10^{-23}$\\
 &  & $\sigma_8$ & $-2.139\times10^{-24}$\\
 \noalign{\smallskip}
 \hline
\end{tabular}
\addtolength{\tabcolsep}{-1pt}
\end{table}

>>>>

{\ny{Just some general comments so that we don't forget:
\begin{itemize}
\item The EoS-insensitive relations are called ``binary Love'', ``I-Love-Q'', ``C-Love'' and ``R-Love.'' There is no need to call them ``binary Love EoS-insensitive relations.'' That's too verbose and not what they are called in the literature. I am ok with describing these relations as EoS-insensitive instead of approximately universal, but let's not change the names. 
\item There is some serious tidying up that needs to be done to all of the text. Specifically, there are missing prepositions, like ``the'', in lots of places that makes the reading a bit choppy and we can improve. Zack, when you have a chance, please do a detail read through and fix the flow as much as you can. 
\item Eventually, we need to discuss the abstract and the intro in more detail. 
\item Let's not forget to check the acknowledgments for funding sources. 
\item Let's do a spell check. 
\item Let's remove all commented out text.  
\end{itemize}
}}
The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities~\cite{Danielewicz:2002pu}), making NSs ideal laboratories for constraining ultra dense nuclear matter.

@@

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also present the relationship between the NS radius and tidal deformability, computed directly from the C-Love relations, showing maximum EoS variability of $358.9 \text{ km}$ from the fit discussed in Sec.~\ref{sec:clove}.
Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love relations will become necessary.
Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal waveform, rather than the PhenomD + 6PN tidal correction to demonstrate the effect of waveform mismodeling.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circles) in the extraction of $\lambda_0$ from GW170817 (O2 detector sensitivity) as if it were observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (turquoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in improved binary Love relations (indigo dashed line) for Voyager CE, and ET.
These results are further tabulated in Table~\ref{tab:variances}.
Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the effect of waveform mismodeling uncertainties.
The single-detection uncertainties are shown by unfilled blue circles, while the combined detection uncertainties are outlined by dashed maroon.
}
\label{fig:stackedFisher}
\end{figure}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.eps}
\end{center}
\caption{
Small representative sets of the unconstrained (dotted) and constrained (solid) EoSs used in this analysis. 
The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constraints applied.
The following restrictions were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.}
\label{fig:eos}
\end{figure}

@@

\begin{table*}
\centering
\caption{
I-Love-Q and C-Love, relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
}\label{tab:ILQfitNew}
\begin{tabular}{ c  c  | c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313$ & $1.287$ & $0.09888$ & $-2.300$ & $-1.347$ & $0.3857$ & $-0.02870$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.555$ & $-2.122$ & $2.72$ & $-1.491$ & $0.8644$ & $-0.1428$ & $-1.397$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.008921$ & $10.59$ & $-37.46$ & $43.18$ & $-2.361$ & $1.967$ & $-0.5678$\\
 $C$ & $\Lambda$ & $-1/5$ & $0.2496$ & $-919.6$ & $330.3$ & $-857.2$ & $-383.5$ & $192.5$ & $-811.1$\\
\hline
\hline
\end{tabular}
\end{table*}

@@

\begin{table}
\centering
\caption{
Comparison between the EoS-insensitive relations (I-Love-Q, C-Love, R-Love, and binary Love) maximal EoS variability for the results of previous works~\cite{Yagi:ILQ,Yagi:binLove}, and the unconstrained and constrained sets of EoSs analyzed here. 
The maximum EoS variation, given by the largest fractional difference (the R-Love variability is shown as the absolute difference in m here) from the fits as shown in Figs.~\ref{fig:ILQ},~\ref{fig:clove},~\ref{fig:rlove} and~\ref{fig:binLove}, observes a considerable improvement for the constrained set of EoSs, compared to the unconstrained set as well as that found in previous works.
Additionally, note how the maximal EoS variation for the unconstrained set of EoSs is slightly larger than that found in Refs.~\cite{Yagi:ILQ,Yagi:binLove} - due to the effects of large random sampling taking into account more sources of uncertainty.
}\label{tab:maxVar}
\begin{tabular}{ c  || c c c } 
 \hline
 \hline
 \textbf{EoS-insensitive} & \multicolumn{3}{c}{\textbf{Maximal EoS Variability}} \\
 \cline{2-4}
 \textbf{Relation} & \multicolumn{1}{c|}{\emph{Previous}} & \multicolumn{1}{c|}{\emph{Unconstrained}} & \emph{Constrained}\\
 \hline
 $\bar{I}-\Lambda$ &  $0.0059$ & $0.007673$ & $0.003138$\\
 $\bar{Q}-\Lambda$ & $0.010$ & $0.01262$ & $0.004661$\\
 $\bar{I}-\bar{Q}$ & $0.012$ & $0.01490$ & $0.005716$\\
 \hline
 $C-\Lambda$ & $0.065$ & $0.07198$ & $0.02169$\\
 $R-\Lambda$ & -- & $358.9 \text{ m}$ & $881.4 \text{ m}$\\
 \hline
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.50$} & \multirow{2}{*}{$0.5724$} & \multirow{2}{*}{$0.2140$}\\
 $(q=0.90)$ & & &\\
 \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.20$} & \multirow{2}{*}{$0.2447$} & \multirow{2}{*}{$0.08284$}\\
  $(q=0.7)$ & & &\\
  \cline{1-1}
 $\Lambda_a-\Lambda_s$ & \multirow{2}{*}{$\sim0.025$} & \multirow{2}{*}{$0.03841$} & \multirow{2}{*}{$0.01823$}\\
  $(q=0.50)$ & & &\\
  \cline{1-1}
\hline
\hline
\end{tabular}
\end{table}

@@

\subsection{C-Love Relations}\label{sec:clove}
In this section we consider approximately EoS-insensitive C-Love relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
Additionally in this section, we compute the relationship between the NS radius and tidal deformability from the C-Love relations.
This allows one to compare the approximate uncertainty on NS radius computed from the C-Love relations for both the constrained and unconstrained sets of EoSs. 
Similar to the previous section, we consider two classes of stars in this section: nuclear matter EoSs and hybrid quark-hadron star EoSs.

@@

In addition, Fig.~\ref{fig:rlove} displays the relationship between the NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
This relationship is computed directly from the C-Love relations discussed above as $R(\Lambda)=m/C(\Lambda)$ for observed mass $m=1.48\text{ M}_{\odot}$ from GW170817.
We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.

\begin{figure}
\begin{center} 
\includegraphics[width=1\columnwidth]{RL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:clove} but for the R-Love relationship between the NS radius and tidal deformability.
This relationship is computed directly from the C-Love relations, and estimates the uncertainty on the NS radius as computed through the C-Love relations.
Observe how the absolute difference from the fit is reduced significantly between the unconstrained and constrained sets of EoSs, shown by the comparisons in Tab.~\ref{tab:maxVar}.
}
\label{fig:rlove}
\end{figure}

@@

\subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.

Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs under the fitting conditions for each case described above. 
We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
From this, we similarly conclude that hybrid stars do obey the C-Love relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.

@@

In this section, we investigate the residuals on $\Lambda_a(\Lambda_s,q)$ in order to marginalize over the intrinsic error found in the binary Love EoS-insensitive relations.
In particular, we restrict our focus to only the constrained set of EoSs.
Residuals in $\Lambda_a$ are computed as $\Lambda_a^{\text{relation}}(\Lambda_s,q)-\Lambda_a^{\text{true}}$, where $\Lambda_a^{\text{true}}$ corresponds to the true value predicted by the sample EoSs, and $\Lambda_a^{\text{relation}}(\Lambda_s,q)$ corresponds to the value obtained through the EoS-insensitive relations found in Sec.~\ref{sec:binLove-nuclear}.
We follow this up by converting the $\Lambda_a$ residuals into $\lambda_0$, allowing us to approximate the overall systematic errors on $\lambda_0$ from using the improved binary Love relations.

Following Ref.~\cite{Katerina:residuals}, we assume the residuals on $\Lambda_a$ observe a Gaussian distribution with mean and standard deviation given by:
\begin{align}
\mu_{\Lambda_a}(\Lambda_s,q) &=\frac{\mu_{\Lambda_s}(\Lambda_s)+\mu_{q}(q)}{2},\\ 
\sigma_{\Lambda_a} &=\sqrt{\sigma_{\Lambda_s}^2(\Lambda_s) + \sigma_{q}^2(q)}. 
\end{align}
Similar to Ref.~\cite{Katerina:residuals}, we fit the individual components to the following power functions:
\begin{align}
\mu_{\Lambda_s}(x) &= \mu_1 x + \mu_2, \label{eq:margFit1}\\ 
\mu_{q}(x) &= \mu_3 x^2 + \mu_4 x + \mu_5, \label{eq:margFit2}\\ 
\sigma_{\Lambda_s}(x) &= \sigma_1 x^{5/2} + \sigma_2 x^{3/2} + \sigma_3 x \sigma_4 x^{1/2} + \sigma_5, \label{eq:margFit3}\\ 
\sigma_{q}(x) &= \sigma_6 x^3 + \sigma_7 x^2 + \sigma_8 x + \sigma_9. \label{eq:margFit4}
\end{align}
The fitting parameters $\mu_i$ and $\sigma_i$ are tabulated in Table~\ref{tab:marginalized}.

\begin{table}
\centering
\caption{
Coefficients to the fits given by Eqs.(~\ref{eq:margFit1})-(\ref{eq:margFit4}) for the relative error on $\Lambda_a$ in the improved binary Love EoS-insensitive relations presented in this paper.
}\label{tab:marginalized}
\addtolength{\tabcolsep}{1pt} 
\begin{tabular}{ c | c || c | c}
\hline 
\noalign{\smallskip}
$\mu_1$ & $3.509 \times 10^{-3}$ & $\sigma_1$ & $-2.074 \times 10^{-7}$\\
$\mu_2$ & $9.351 \times 10^{-1}$ & $\sigma_2$ & $-1.492 \times 10^{-3}$\\
$\mu_3$ & $-18.07$ & $\sigma_3$ & $-4.891 \times 10^{-2}$\\
$\mu_4$ & $27.56$ & $\sigma_4$ & $8.207 \times 10^{-1}$\\
$\mu_5$ & $-10.10$ & $\sigma_5$ & $-1.308$\\
 &  & $\sigma_6$ & $-63.76$\\
 &  & $\sigma_7$ & $11.14$\\
 &  & $\sigma_8$ & $75.25$\\
 &  & $\sigma_8$ & $-23.69$\\
 \noalign{\smallskip}
 \hline
\end{tabular}
\addtolength{\tabcolsep}{-1pt}
\end{table}
